---
title: "Compare Many Groups"
output: 
    pdf_document: default
    geometry: margin=3in
params:
  m: NA
  m1: NA
  c: NA
  p: NA
  p1: NA
  r: NA
  pt: NA
  rr: NA

---

**Date:** `r format(Sys.time(), "%d %B, %Y")`.
<br/>
\
&nbsp;

**Method**:  `r params$m`  

**Data**: `r params$c`<br/>
\
&nbsp;

**Normality Test** (`r params$m1`):  **P-value** = `r params$p`   (`r if(params$p>=0.05){"Paased"} else{"Failed"}`)<br/>

**Equal Variance Test** (Levene's Test):  **P-value** = `r params$p1` (`r if(params$p1>=0.05){"Paased"} else{"Failed"}`)<br/>
\
&nbsp;<br/>

Result:
\
&nbsp;<br/>
`r options(digits=5)`
`r if(params$m=="One Way ANOVA" && (params$p<0.05 || params$p1<0.05)){"Because of the Normality/Equal Variance Test P-value, Statitic Analysis is transfered to ANOVA on Ranks..."}`
\
&nbsp;<br/>
```{r,echo=FALSE} 
params$r 
options(digits=6)
```
<br/>
\
&nbsp;
\
&nbsp;

`r if(params$m=="One Way ANOVA" && params$p>=0.05 && params$p1>=0.05 && params$pt<0.05){paste("The differences in the mean values among the treatment groups are greater than would be expected by chance; there is a statistically significant difference (P = ",round(params$pt,4)," )","\n","\n","Multiple Comparisons versus Control Group","\n")} else if(params$m=="One Way ANOVA" && params$p>=0.05 && params$p1>=0.05 && params$pt>=0.05){paste("The differences in the mean values among the treatment groups are not greater than would be expected by chance; there is not a statistically significant difference (P = ",round(params$pt,4)," ).","\n","\n")}`

<br/>


`r if((params$p<0.05 || params$p1<0.05) && params$pt<0.05){paste("The differences in the median values among the treatment groups are greater than would be expected by chance; there is a statistically significant difference (P = ",round(params$pt,4)," )","\n","\n","Multiple Comparisons versus Control Group","\n")} else if((params$p<0.05 || params$p1<0.05) && params$pt>=0.05){paste("The differences in the median values among the treatment groups are not greater than would be expected by chance; there is not a statistically significant difference (P = ",round(params$pt,4)," )","\n","\n")}`

<br/>
\
&nbsp;

```{r,echo=FALSE}
if(params$pt<0.05){
  params$rr}
options(digits=6)
```




